Modelling BCG vaccination in the UK

### 2019-05-03 rmds/05-evidence-policy-change.Rmd
reorganised thesis to work with online gitbook
Former-commit-id: 3fd8c59438bc22ef6b09d75159886a79ea855f4e

## Read formated results
## See https://github.com/seabbs/AssessBCGPolicyChange/blob/master/vignettes/paper.Rmd
## for code required to reproduce 
## Chapter is an edited version of the orginal reproducible document.
## Original results found at: https://github.com/seabbs/AssessBCGPolicyChange/blob/master/vignettes/results/paper
## Original figures found at: https://github.com/seabbs/AssessBCGPolicyChange/blob/master/docs/articles/paper_files/figure-html
##Wordcount:

>>>>

## Read formated results
## See https://github.com/seabbs/AssessBCGPolicyChange/blob/master/vignettes/paper.Rmd
## for code required to reproduce 
## Chapter is an edited version of the orginal reproducible document.
## Original results found at: https://github.com/seabbs/AssessBCGPolicyChange/blob/master/vignettes/results/paper
## Original figures found at: https://github.com/seabbs/AssessBCGPolicyChange/blob/master/docs/articles/paper_files/figure-html
##Wordcount: 4249

### 2019-05-03 rmds/index.Rmd
reorganised thesis to work with online gitbook
Former-commit-id: 3fd8c59438bc22ef6b09d75159886a79ea855f4e

---
output: html_document
---

```{r}
## Wordcount: 2811
```

>>>>

---
author: 'Samuel Abbott'
date: 'May 2019'
division: 'Bristol Medical School: Population Health Sciences'
advisor: 'Ellen Brooks Pollock'
altadvisor: 'Hannah Christensen'
department: 'Faculty of Health Sciences'
title: 'Modelling BCG vaccination in the UK'
subtitle: 'What is the impact of changing policy?'
wordcount: "41,218"
knit: bookdown::render_book
site: bookdown::bookdown_site
always_allow_html: yes
output: 
  #thesisdown::thesis_pdf: default
  thesisdown::thesis_gitbook: default
  #thesisdown::thesis_word: default
  #thesisdown::thesis_epub: default
abstract: >
  `r if(knitr:::is_latex_output()) paste(readLines("00-abstract.Rmd"), collapse = ' ')`
acknowledgements: >
 `r if(knitr:::is_latex_output()) paste(readLines("00-acknowledgements.Rmd"), collapse = ' ')`
declaration: >
  `r if(knitr:::is_latex_output()) paste(readLines("00-declaration.Rmd"), collapse = ' ')`
contribution: >
  `r if(knitr:::is_latex_output()) paste(readLines("00-contribution.Rmd"), collapse = ' ')`
bibliography: bib/thesis.bib
#Download your specific bibliography database file and refer to it in the line above.
csl: csl/bmj.csl
#Download your specific csl file and refer to it in the line above.
lot: true
lof: true
space_between_paragraphs: true
#Delete the # at the beginning of the previous line if you'd like
#to have a blank new line between each paragraph
link-citations: yes
colorlinks: yes
description: "A dissertation submitted to the University of Bristol in accordance with the requirements for award of the degree of Doctor of Philosophy in the Faculty of Health Sciences. This dissertation explores the use of the BCG vaccine for Tuberculosis control in England."
url: 'https\::/samabbott.co.uk/thesis/'
github-repo: seabbs/thesis
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage[table]{xcolor}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
---

```{r knitr-options, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, dpi = 320, 
                      fig.width = 8, fig.height = 8,
                      out.width = "80%", fig.align = 'center')
```

```{r include_packages, include = FALSE}
if (!require(devtools))
  install.packages("devtools", repos = "http://cran.rstudio.com")
if (!require(thesisdown))
  devtools::install_github("ismayc/thesisdown")
library(thesisdown)
if (!require(tidyverse))
  install.packages("tidyverse", repos = "http://cran.rstudio.com")
PaperTheme <- ggplot2::theme_minimal() +
  theme(legend.position = "top")
ggplot2::theme_set(PaperTheme)
```
